---
title: "Third Week: Exploratory Data Analysis"
author: "student name"
subtitle: "LaLiga Analysis"
date: "`r Sys.time()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---



```{r}
knitr::opts_chunk$set(echo = TRUE,comment = "",error = F,message = F,
                      warning = F,fig.width = 10,fig.height = 6,fig.align = "center")
library(engsoccerdata)
library(dplyr)
library(ggplot2)
library(highcharter)
```

1-

```{r}
rbind(
  spain %>%
    select(Season, team = home, opp = visitor, GF = hgoal, GA = vgoal),
  spain %>%
    select(Season, team = visitor, opp = home, GF = vgoal, GA = hgoal)
) %>% mutate(GD = GF-GA) %>% 
  group_by(team,Season) %>% 
    summarize(GP = n(),
            goalsF = sum(GF),
            goalsA = sum(GA),
            goaldif = sum(GD),
            W = sum(GD>0),
            D = sum(GD==0),
            L = sum(GD<0)
  ) %>% 
  mutate(score = W*3 + D) %>%
  arrange(Season,desc(score),desc(goaldif),desc(goalsF)) %>% 
  group_by(Season) %>% 
  mutate(rank = row_number(-score) %>% as.integer()) -> lig
lig %>% group_by(team) %>% 
  summarise(champ_num = sum(rank==1)) %>% 
  arrange(desc(champ_num)) -> f_lig
f_lig

#### plot
f_lig %>% 
  hchart(type = "column",hcaes(x = team, y = champ_num),name = "score")
f_lig %>%
  ggplot()+geom_bar(aes(x = team , y = champ_num) , stat = "identity")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



2- 


```{r}
lig <- ungroup(lig)
lig %>% group_by(team) %>% 
  summarise(kesel = sum(goalsF))%>% 
  arrange(kesel) %>% 
  slice(1:10) -> kesel_team
kesel_team %>% 
   hchart(type = "column",hcaes(x = team, y = kesel ),name = "score")

lig %>% 
  group_by(Season) %>%
  summarise(kesel = sum(goalsF + goalsA)) %>% 
  arrange(kesel) %>% 
  slice(1:10) -> kesel_season
kesel_season %>% 
   hchart(type = "column",hcaes(x = Season, y = kesel ),name = "score")

```

3- 


```{r}
rbind(
  spain %>%
    select(Date ,Season, team = home, opp = visitor, GF = hgoal, GA = vgoal),
  spain %>%
    select(Date ,Season, team = visitor, opp = home, GF = vgoal, GA = hgoal)
) %>% mutate(GD = GF-GA) %>%  
    mutate(W = ifelse(GD > 0,1,0),
    D = ifelse(GD == 0,1,0),
    L = ifelse(GD < 0,1,0)
) %>% group_by(Season,team) %>%
  arrange(Date) %>% 
  mutate(play = row_number(Date)) -> season
  season %>% group_by(Season,team) %>% 
    mutate(goalsF = cumsum(GF),
      goalsA = cumsum(GA),
      goaldif = cumsum(GD),
      W = cumsum(W),
      D = cumsum(D),
      L = cumsum(L)
  ) %>% 
  mutate(score = W*3 + D) %>% arrange(team,play) -> history
########### finds final leag
  history %>% 
  filter(play == max(play)) %>% 
  arrange(Season,desc(score),desc(goaldif),desc(goalsF)) %>% 
  group_by(Season) %>% 
  mutate(rank = row_number(-score) %>% as.integer()) %>% 
  filter(rank ==1 ) %>% 
  select(Season,team) -> lig_final
######### find 
history %>% 
  filter(play == max(play)/2) %>% 
  arrange(Season,desc(score),desc(goaldif),desc(goalsF)) %>% 
  group_by(Season) %>% 
  mutate(rank = row_number(-score) %>% as.integer()) %>% 
  filter(rank == 1 ) %>% 
  select(Season,team)-> lig_nim

sum(lig_nim$team == lig_final$team)/nrow(lig_final)

```
 i find lig_nim and lig_final table and find winner of each in each season . then campare them :)


4- 
to find black cat i will find teams that can win 4 best teams in one season . (Real Madrid , Fc barcelona , Athletic Bilbao , Atletico Madrid) . 
actully each team had 8 game with these  that if can win 4 of them it will be black cat in my opinion :)

```{r}
#### creat new list that in each row we just see the result of that game not sum of all games played by that team.
rbind(
  spain %>%
    select(Date , Season, team = home, opp = visitor, GF = hgoal, GA = vgoal),
  spain %>%
    select(Date , Season, team = visitor, opp = home, GF = vgoal, GA = hgoal)
) %>% mutate(GD = GF-GA) %>%  
    mutate(W = ifelse(GD > 0,1,0),
    D = ifelse(GD == 0,1,0),
    L = ifelse(GD < 0,1,0)
) %>% arrange(Date) -> win_table

win_table %>% 
  filter((Season<=2010) & (Season>=2001)) %>% 
  group_by(Season) %>% 
  filter((opp %in% c("FC Barcelona","Athletic Bilbao","Real Madrid","Atletico Madrid"))) %>% 
  filter(!(team %in% c("FC Barcelona","Athletic Bilbao","Real Madrid","Atletico Madrid"))) %>% 
  group_by(team,Season) %>%
  summarise(big_team_win = sum(W)) %>% 
  arrange(-big_team_win)
  
```

as you can see "Villarreal CF" win 6 of 8 game with big team on 2007 suddenly without before achivment . Real Sociedad with 5 wining is another black cat team . 
you can verify "Sevilla FC" and "CA Osasuna" but they repeat their achivment maybe they can not be black cat .


5- 
```{r}
history %>%
  arrange(Season,desc(score),desc(goaldif),desc(goalsF)) %>% 
  group_by(Season) %>% 
  mutate(m_play = max(play))%>% 
  group_by(Season,play) %>% 
  mutate(rank_play = row_number(-score) %>% as.integer()) %>% 
  filter(sort(score,decreasing=T)[1]-sort(score,decreasing=T)[2] > (3*(m_play-play)))%>% 
  arrange(wini_diff = -m_play + play) %>% 
  filter(rank_play==1) %>% slice(1)
```

```{r}
  history %>% 
  filter(play == max(play)) %>% 
  arrange(Season,desc(score),desc(goaldif),desc(goalsF)) %>% 
  group_by(Season) %>% 
  summarize(winner_diff = sort(score,decreasing=T)[1]-sort(score,decreasing=T)[2]) -> 
  win_diff_sea

  ### find season with max winner diffrention :)
lig_final$team[which.max(win_diff_sea$winner_diff)]
    
```




6- 

```{r}
####### find max repeated seq in x vector
find_max_rep <- function(x){
  max_rep <- 1;
  rep <- 1;
  for (i in 1:(length(x)-1)){
    if ((x[i] == 1) && (x[i+1] == 1))
      rep <- rep + 1
    else{
      if(rep > max_rep){
        max_rep <- rep
      }
      rep <- 1
    }
  }
  if(rep > max_rep){
        max_rep <- rep
      }
  return(max_rep)
}

  

```
here i will find bigest replicated seq in wining :and then find best team
```{r}
win_table %>% 
  group_by(team) %>% 
  summarise(count = find_max_rep(W)) %>% 
  arrange(-count) %>% 
  slice(1)

```
for DEFEAT :
```{r}
win_table %>% 
  group_by(team) %>% 
  summarise(count = find_max_rep(L)) %>% 
  arrange(-count) %>% 
  slice(1)
```
for EQUAL :
```{r}
win_table %>% 
  group_by(team) %>% 
  summarise(count = find_max_rep(D)) %>% 
  arrange(-count) %>% 
  slice(1)

```



7- 


```{r}
history %>%
  arrange(Season,desc(score),desc(goaldif),desc(goalsF)) %>% 
  group_by(Season) %>% 
  mutate(m_play = max(play))%>% 
  group_by(Season,play) %>% 
  mutate(rank_play = row_number(-score) %>% as.integer()) %>% 
  filter(sort(score)[4]-sort(score)[1] > (3*(m_play-play)))%>% 
  arrange(wini_diff = - m_play + play)  %>% 
  filter(rank_play == max(rank_play)) %>% 
  .[1,]                            
  
```





8- 
```{r}
history %>%
  filter(Season==1998) %>% 
  arrange(Season,desc(score),desc(goaldif),desc(goalsF)) %>% 
  group_by(Season) %>% 
  mutate(m_play = max(play))%>% 
  group_by(Season,play) %>% 
  mutate(rank_play = row_number(-score) %>% as.integer()) -> week_tbl

week_tbl  %>% arrange(play) %>% 
  hchart(type = "line",hcaes(x = play, y = rank_play, group = team))

```